Single-cell virus sequencing of influenza variants that trigger innate immunity

### 2018-09-06 paper/paper.tex
Working on methods section, still rough

\subsection{IFN reporter cell lines}
\jdbcomment{Alistair writes this}
Reporter sequences \FIGDATA[IFNrare]{reporter_sequences}

\subsection{Viral stocks}
\jdbcomment{Alistair writes this}
Wildtype and synonymously barcoded viruses in \FIGDATA[experiment]{virus_seqs}

>>>>

\subsection{IFN reporter cell lines}
\jdbcomment{Alistair writes this}
For our type I interferon reporters, A 1kb region upstream of the human IFNB1 gene was cloned into the pHAGE2 lentiviral vector, with a NotI site immediately downstream serving as an artificial kozak sequence (REF). 
Downstream of this NotI site, each of the following reporter constructs was cloned: mCherry, mNeongreen, and mNeongreen translationally linked to LNGFR$\delta$C by a p2A linker (REFS).
For our type III interferon reporters, a 1.2kb region upstream of the human IL29 (IFNL1) gene was cloned into the pHAGE2 vector, with the native kozak sequence left at the 3' end. 
Downstream of this promoter zsGreen translationally linked to LNGFR$\delta$C via a p2A linker was cloned. 
Replication-incompetent lentivirus was generated from these vectors as previously described (REF).
A monolayer of A549 cells was transduced with each lentivirus, and sorted as single cells. 
These single cell clones were grown and tested for reporter activity by poly I:C transfection ? a potent agonist of the RIG-I pathway.
Critically, cells propagated and used in experiments were not exposed to poly I:C,  thus avoiding selection on survival post interferon-induction.
For our dual- type I and type III reporter, a single-cell clone of our type III reporter strain was transduced with our type I reporter bearing the mCherry fluorescent marker and subsequently propagated as a single cell clone and validated as above.

Reporter sequences \FIGDATA[IFNrare]{reporter_sequences}

\subsection{Viral stocks}
\jdbcomment{Alistair writes this}
All viruses were generated using reverse-genetics as previously described.
Briefly, bidirectional plasmids producing viral mRNA and vRNA are transfected into a co-culture of MDCK-SIAT1 and 293t cells grown in D10.
After 24h, media is changed from D10 to influenza growth media.
Between 48h and 72h post-infection, depending on viral growth kinetics, supernatant is harvested and titered by TCID50.
Virus is subsequently expanded on MDCK-SIAT1 cells as described below.
For all viral variants, the described mutations were introduced into reverse-genetics plasmids using PCR mutagenesis. 
For the HA-flanked mCherry pseudovirus, a plasmid was generated similarly to a previously-described HA-flanked eGFP vector.
Synonymously-barcoded virus utilized previously described 3' synonymous mutations, and two newly-introduced single-nucleotide synonymous mutations at the 5' end of each viral gene.
Wild-type, synonymously-barcoded, NS1-inactivated, and single-nucleotide variant viruses were all grown in unmodified MDCK-SIAT1 and 293t cells.
Viral variants bearing large internal deleltions in the PB1 segment were grown in MDCK-SIAT1 and 293t cells expressing PB1 as previously described.
Pseudovirus expressing mCherry in place of eGFP was grown in MDCK-SIAT1 and 293t cells expressing HA as previously described.

Wildtype and synonymously barcoded viruses in \FIGDATA[experiment]{virus_seqs} obtained from reverse-genetic transfections was subsequently propagated at an MOI of 0.001 for 72h twice in MDCK-SIAT1 cells (wild-type) or once at an MOI of 0.01 (barcoded) for 60h in order to generate potential immunostimulatory diversity.
For analyses of interferon induction, an additional wild-type stock of virus was grown at an MOI of 0.01 for 36h in order to generate a population relatively free of defective particles. (WILL REPEAT WITH 48H STOCK AS DESCRIBED BELOW)
Viruses bearing SNPs, deletions in PB1, NS1-inactivation mutations, and HA-mCherry pseudovirus were all propagated at an MOI of 0.01 for 48h owing to slower growth kinetics. 
All stocks were subsequently titered by TCID50, using complementing cells where necessary.
Additionally, for qPCR experiments, stocks were titered by qPCR against the viral HA segment using a plasmid standard to determine relative genome copy numbers between viral stocks.
